---
title: "apd lapd exploration"
author: "Nick Hoffman"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    highlight: pygment
    keep_md: no
    toc: true
    number_sections: true
    toc_depth: 1
    toc_float: true
    theme: journal
editor_options:
    chunk_output_type: inline
---

<style type="text/css">
h2, h3, h4, h5, h6 {
  counter-reset: section;
}
p {
  font-size:18px;
}

ul {
  font-size:18px;
}

li {
  font-size:18px;
}
table {
   padding: 0;border-collapse: collapse;
   layout: fixed;
   width: 90%; }
table tr {
   border-top: 1px solid #cccccc;
   background-color: white;
   margin: 0;
   padding: 0; }
table tr:nth-child(2n) {
   background-color: #f8f8f8; }
table tr th {
   font-weight: bold;
   border: 1px solid #cccccc;
   margin: 0;
   padding: 6px 13px; }
table tr td {
   border: 1px solid #cccccc;
   margin: 0;
   padding: 6px 13px; }
table tr th :first-child, table tr td :first-child {
   margin-top: 0; }
table tr th :last-child, table tr td :last-child {
   margin-bottom: 0; }
.html-widget {
    margin: auto;
}
</style>

---

```{r, results='asis', echo = F}
toc_depth <- rmarkdown::metadata$output$html_document$toc_depth
sel <- paste0("h",(toc_depth+1):10, collapse = " > span, ")
cat(paste0("<style>",
           sel, 
           " > .header-section-number { display: none; } </style>"))
```

```{r setup,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(neotoma2)
library(DT)
library(tidyverse)
library(httr)
library(ggplot2)
library(lubridate)
```



```{r cars,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}

db_sets = as.data.frame(matrix(nrow=0,ncol=7))
names(db_sets) =c("lon","lat","siteid","sitename","datasetid","datasettype","dbID")
for (i in c(2,5)) {
 db = content(GET(paste0("https://api.neotomadb.org/v2.0/apps/constdb/datasets?dbid=",i)))$data
    #print(paste("DB ID:",i))
    db_mat = matrix(nrow=length(db),ncol=7)
    for (m in seq(length(db))) {
      if(!is.null(db[[m]]$coords[[1]])) {
        db_mat[[m,1]] = db[[m]]$coords[[1]]}
      if(!is.null(db[[m]]$coords[[2]])) {
        db_mat[[m,2]] = db[[m]]$coords[[2]]}
      if(!is.null(db[[m]]$siteid)) {
        db_mat[[m,3]] = db[[m]]$siteid}
      if(!is.null(db[[m]]$sitename)) {
        db_mat[[m,4]] = db[[m]]$sitename}
      if(!is.null(db[[m]]$datasetid)) {
        db_mat[[m,5]] = db[[m]]$datasetid
      }
        if(!is.null(db[[m]]$datasettype)) {
        db_mat[[m,6]] = db[[m]]$datasettype
        }
      db_mat[[m,7]] = i
    }
    db_df = as.data.frame(db_mat)
    names(db_df) = c("lon","lat","siteid","sitename","datasetid","datasettype","dbID")
    db_sets = rbind(db_sets,db_df)

}

```

# Data Tables

Below are the data tables for the LAPD and APD.

## Collection Units

```{r pressure,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}
collunits = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/collectionunits?count=false&limit=99999"))$data


collunits_mat = matrix(nrow=length(collunits),ncol=20)

for (i in seq(length(collunits))) {
  for(j in seq(20) ) {
    if (!is.null(collunits[[i]][[j]])) {
  collunits_mat[i,j] = collunits[[i]][[j]]
    }}}


collunits_df = as.data.frame(collunits_mat)


names(collunits_df) = c("collectionunitid","handle","siteid","colltypeid","depenvtid","collunitname","colldate","colldevice","gpslatitude","gpslongitude","gpsaltitude","gpserror","waterdepth","substrateid","slopeaspect","slopeangle","location","notes","recdatecreated","recdatemodified")

alapd_colls = collunits_df %>% dplyr::filter(siteid %in% db_sets$siteid)


datatable(alapd_colls,rownames=FALSE)
```


## Sites

```{r site,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}
sites = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/sites?count=false&limit=99999"))$data



site_mat = matrix(nrow=length(sites),ncol=13)

for (i in seq(length(sites))) {
  for(j in seq(13) ) {
    if (!is.null(sites[[i]][[j]])) {
  site_mat[i,j] = sites[[i]][[j]]
    }}}


site_df = as.data.frame(site_mat)


names(site_df) = c("siteid","sitename","longitudeeast","latitudenorth","longitudewest","latitudesouth","altitude","area","sitedescription","notes","datecreated","datemodified","geog")
alapd_sites = site_df %>% dplyr::filter(siteid %in% db_sets$siteid)

datatable(alapd_sites,rownames=FALSE)
```


## Datasets

```{r dataste,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}
datasets = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/datasets?count=false&limit=99999"))$data



dataset_mat = matrix(nrow=length(datasets),ncol=8)

for (i in seq(length(datasets))) {
  for(j in seq(8) ) {
    if (!is.null(datasets[[i]][[j]])) {
  dataset_mat[i,j] = datasets[[i]][[j]]
    }}}


dataset_df = as.data.frame(dataset_mat)


names(dataset_df) = c("datasetid","collectionunitid","datasettypeid","datasetname","notes","datecreated","datemodified","embargoid")
alapd_datasets = dataset_df %>% dplyr::filter(datasetid %in% db_sets$datasetid)

datatable(alapd_datasets,rownames=FALSE)
```


## Samples

```{r samples,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}
samples1 = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/samples?count=false&limit=99999"))$data

samplesb = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/samples?count=false&offset=99999&limit=100000"))$data
samples2 = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/samples?count=false&offset=199999&limit=99999"))$data
samples3 = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/samples?count=false&offset=299998&limit=99999"))$data
samples4 = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/samples?count=false&offset=399997&limit=99999"))$data
samples5 = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/samples?count=false&offset=499996&limit=99999"))$data

samples = append(samples1,samplesb) %>% append(samples2) %>% append(samples3) %>% append(samples4) %>% append(samples5) 

sample_mat = matrix(nrow=length(samples),ncol=12)

for (i in seq(length(samples))) {
  for(j in seq(12) ) {
    if (!is.null(samples[[i]][[j]])) {
  sample_mat[i,j] = samples[[i]][[j]]
    }}}


sample_df = as.data.frame(sample_mat)


names(sample_df) = c("sampleid","analysisunitid","datasetid","samplename","analysisdate","labnumber","preparationmethod","sample_notes","datecreated","datemodified","sampledate","taxonid")
alapd_samples = sample_df %>% dplyr::filter(datasetid %in% db_sets$datasetid)

datatable(alapd_samples,rownames=FALSE)
```


## Analysis Units

```{r analysisunits,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}
analysisunits1 = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/analysisunits?count=false&limit=99999"))$data

analysisunits2 = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/analysisunits?count=false&limit=99999&offset=99999"))$data
analysisunits3 = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/analysisunits?count=false&limit=99999&offset=199998"))$data
analysisunits4 = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/analysisunits?count=false&limit=99999&offset=299997"))$data
analysisunits5 = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/analysisunits?count=false&limit=99999&offset=399996"))$data


analysisunits = append(analysisunits1,analysisunits2) %>% append(analysisunits3) %>% append(analysisunits4) %>% append(analysisunits5)


analysis_mat = matrix(nrow=length(analysisunits),ncol=11)

for (i in seq(length(analysisunits))) {
  for(j in seq(11) ) {
    if (!is.null(analysisunits[[i]][[j]])) {
  analysis_mat[i,j] = analysisunits[[i]][[j]]
    }}}


analysis_df = as.data.frame(analysis_mat)


names(analysis_df) = c("analysisunitid","collectionunitid","analysisunitname","depth","thickness","faciesid","mixed","igsn","notes","datecreated","datemodified")

analysis_join = analysis_df %>% dplyr::left_join(collunits_df,by=join_by("collectionunitid"))
alapd_analysisunits = analysis_join %>% dplyr::filter(siteid %in% db_sets$siteid)

datatable(alapd_analysisunits[1:11],rownames=FALSE)
```


## Publications

```{r pubs,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}
pubs = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/publications?count=false&limit=99999"))$data



pub_mat = matrix(nrow=length(pubs),ncol=26)

for (i in seq(length(pubs))) {
  for(j in seq(26) ) {
    if (!is.null(pubs[[i]][[j]])) {
  pub_mat[i,j] = pubs[[i]][[j]]
    }}}


pub_df = as.data.frame(pub_mat)


names(pub_df) = c("publicationid","pubtypeid","year","citation","articletitle","journal","volume","issue","pages","citationnumber","doi","booktitle","numvolumes","edition","volumetitle","seriestitle","seriesvolume","publisher","url","city","state","country","originallanguage","notes","datecreated","datemodified")


datpubs = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/datasetpublications?count=false&limit=99999"))$data



datpub_mat = matrix(nrow=length(datpubs),ncol=5)

for (i in seq(length(datpubs))) {
  for(j in seq(5) ) {
    if (!is.null(datpubs[[i]][[j]])) {
  datpub_mat[i,j] = datpubs[[i]][[j]]
    }}}


datpub_df = as.data.frame(datpub_mat)


names(datpub_df) = c("datasetid","publicationid","primarypub","datecreated","datemodified")

alapd_datpubs = pub_df %>% left_join(datpub_df, by=join_by("publicationid")) %>% dplyr::filter(datasetid %in% db_sets$datasetid)

datatable(alapd_datpubs,rownames=FALSE)
```

# Total Misses

Below are tables of the total number of missing values for each field from the above tables.

## Collection Units


```{r total-misses,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}

missing_colls =alapd_colls %>% left_join(db_sets, by=join_by(siteid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename,datasetid,datasettype,dbID)) %>% distinct() %>% group_by(db) %>% summarize_all(~ sum(is.na(.)))


collcount =alapd_colls %>% left_join(db_sets, by=join_by(siteid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename,datasetid,datasettype,dbID)) %>% distinct() %>% group_by(db) %>% count()

missing_colls = as.data.frame(t(missing_colls))
names(missing_colls) = c("african pollen db", "latin american pollen db")

datatable(collcount,rownames=FALSE)


datatable(missing_colls)

```

## Sites

``` {r sitemis,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}

missing_sites =alapd_sites %>% left_join(db_sets, by=join_by(siteid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename.y,datasetid,datasettype,dbID)) %>%  distinct() %>% group_by(db) %>% summarize_all(~ sum(is.na(.)))

sitecount = alapd_sites %>% left_join(db_sets, by=join_by(siteid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename.y,datasetid,datasettype,dbID)) %>%  distinct() %>% group_by(db) %>% count()



missing_sites = as.data.frame(t(missing_sites))
names(missing_sites) = c("african pollen db", "latin american pollen db")


datatable(sitecount,rownames=FALSE)


datatable(missing_sites)

```

## Datasets

```{r datemis,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}
missing_datasets =alapd_datasets %>%  left_join(db_sets, by=join_by(datasetid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename,datasetid,datasettype,dbID)) %>%  distinct() %>% group_by(db) %>% summarize_all(~ sum(is.na(.)))

datasetcount = alapd_datasets %>%  left_join(db_sets, by=join_by(datasetid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename,datasetid,datasettype,dbID)) %>%  distinct() %>% group_by(db) %>% count()


missing_datasets = as.data.frame(t(missing_datasets))
names(missing_datasets) = c("african pollen db", "latin american pollen db")


datatable(datasetcount,rownames=FALSE)

datatable(missing_datasets)

```

## Samples

```{r samplmiss,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}

missing_samples =alapd_samples %>% left_join(db_sets, by=join_by(datasetid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename,datasetid,datasettype,dbID)) %>%  distinct() %>% group_by(db) %>% summarize_all(~ sum(is.na(.)))

samplecount = alapd_samples %>% left_join(db_sets, by=join_by(datasetid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename,datasetid,datasettype,dbID)) %>%  distinct() %>% group_by(db) %>% count()


missing_samples = as.data.frame(t(missing_samples))
names(missing_samples) = c("african pollen db", "latin american pollen db")



datatable(samplecount,rownames=FALSE)

datatable(missing_samples)


```

## Analysis Units

```{r analysmis,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}

missing_analysisunits =alapd_analysisunits %>% left_join(db_sets, by=join_by(siteid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(handle,siteid,colltypeid,depenvtid,collunitname,colldate,colldevice,gpslatitude,gpslongitude,gpsaltitude,gpserror,waterdepth,substrateid,slopeaspect,slopeangle,location,notes.y,recdatecreated,recdatemodified,lon,lat,sitename,datasetid,datasettype,dbID)) %>% distinct() %>% group_by(db) %>% summarize_all(~ sum(is.na(.)))

analycount = alapd_analysisunits %>% left_join(db_sets, by=join_by(siteid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(handle,siteid,colltypeid,depenvtid,collunitname,colldate,colldevice,gpslatitude,gpslongitude,gpsaltitude,gpserror,waterdepth,substrateid,slopeaspect,slopeangle,location,notes.y,recdatecreated,recdatemodified,lon,lat,sitename,datasetid,datasettype,dbID)) %>% distinct() %>% group_by(db) %>% count()


missing_analysisunits = as.data.frame(t(missing_analysisunits))
names(missing_analysisunits) = c("african pollen db", "latin american pollen db")



datatable(analycount,rownames=FALSE)

datatable(missing_analysisunits)

```

## Publications

```{r pubmiss,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}

missing_publications =alapd_datpubs %>% left_join(db_sets, by=join_by(datasetid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(datasetid,primarypub,datecreated.y,datemodified.y,lon,lat,sitename,datasetid,datasettype,dbID)) %>%  distinct() %>% group_by(db) %>% summarize_all(~ sum(is.na(.)))


pubcount = alapd_datpubs %>% left_join(db_sets, by=join_by(datasetid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(datasetid,primarypub,datecreated.y,datemodified.y,lon,lat,sitename,datasetid,datasettype,dbID)) %>%  distinct() %>% group_by(db) %>% count()


missing_publications = as.data.frame(t(missing_publications))
names(missing_publications) = c("african pollen db", "latin american pollen db")


datatable(pubcount,rownames=FALSE)


datatable(missing_publications)
```

# Misses Over Time

Below are graphs of the cumulative sum of misses for each of the fields shown above, ordered by year-month.

## Collection Units

```{r change-in-time,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}


missing_colls_t =alapd_colls %>% left_join(db_sets, by=join_by(siteid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename,datasetid,datasettype,dbID)) %>% distinct() %>% mutate(date = as.Date(recdatecreated)) %>%  mutate(year_month = floor_date(date, unit = "month")) %>% group_by(db,year_month) %>% summarize_all(~ sum(is.na(.))) %>% mutate_if(is.numeric, cumsum) %>% pivot_longer(cols=c(3:22),names_to = "parameter",values_to = "num_missing")

ggplot(missing_colls_t) + 
  geom_line(mapping=aes(x=year_month,y=num_missing,col=db)) + 
  facet_wrap(~parameter) + theme_bw()

```

## Sites

```{r timesitemis,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}



missing_sites_t =alapd_sites %>% left_join(db_sets, by=join_by(siteid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename.y,datasetid,datasettype,dbID)) %>% distinct() %>% mutate(date = as.Date(datecreated)) %>%  mutate(year_month = floor_date(date, unit = "month")) %>% group_by(db,year_month) %>%  summarize_all(~ sum(is.na(.))) %>% mutate_if(is.numeric, cumsum) %>% pivot_longer(cols=c(3:15),names_to = "parameter",values_to = "num_missing")

ggplot(missing_sites_t) + 
  geom_line(mapping=aes(x=year_month,y=num_missing,col=db)) + 
  facet_wrap(~parameter) + theme_bw()



```

## Datasets

``` {r timedatmis,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}

missing_datasets_t =alapd_datasets %>%  left_join(db_sets, by=join_by(datasetid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename,datasetid,datasettype,dbID)) %>% distinct() %>% mutate(date = as.Date(datecreated)) %>%  mutate(year_month = floor_date(date, unit = "month")) %>% group_by(db,year_month) %>%  summarize_all(~ sum(is.na(.))) %>% mutate_if(is.numeric, cumsum) %>% pivot_longer(cols=c(3:9),names_to = "parameter",values_to = "num_missing")

ggplot(missing_datasets_t) + 
  geom_line(mapping=aes(x=year_month,y=num_missing,col=db)) + 
  facet_wrap(~parameter) + theme_bw()


```

## Samples

``` {r timesamplemiss,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}

missing_samples_t =alapd_samples %>% left_join(db_sets, by=join_by(datasetid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(lon,lat,sitename,datasetid,datasettype,dbID)) %>% distinct() %>% mutate(date = as.Date(datecreated)) %>%  mutate(year_month = floor_date(date, unit = "month")) %>% group_by(db,year_month) %>%  summarize_all(~ sum(is.na(.))) %>% mutate_if(is.numeric, cumsum) %>% pivot_longer(cols=c(3:13),names_to = "parameter",values_to = "num_missing")


ggplot(missing_samples_t) + 
  geom_line(mapping=aes(x=year_month,y=num_missing,col=db)) + 
  facet_wrap(~parameter) + theme_bw()


```

## Analysis Units

```{r analysistimemiss,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}
missing_analysisunit_t = alapd_analysisunits %>% left_join(db_sets, by=join_by(siteid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(handle,siteid,colltypeid,depenvtid,collunitname,colldate,colldevice,gpslatitude,gpslongitude,gpsaltitude,gpserror,waterdepth,substrateid,slopeaspect,slopeangle,location,notes.y,recdatecreated,recdatemodified,lon,lat,sitename,datasetid,datasettype,dbID)) %>% distinct() %>% mutate(date = as.Date(datecreated)) %>%  mutate(year_month = floor_date(date, unit = "month")) %>% group_by(db,year_month) %>% summarize_all(~ sum(is.na(.))) %>% mutate_if(is.numeric, cumsum) %>% pivot_longer(cols=c(3:13),names_to = "parameter",values_to = "num_missing")

ggplot(missing_analysisunit_t) + 
  geom_line(mapping=aes(x=year_month,y=num_missing,col=db)) + 
  facet_wrap(~parameter) + theme_bw()

```

## Publications

```{r pubtimemiss,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}
missing_publications_t = alapd_datpubs %>% left_join(db_sets, by=join_by(datasetid)) %>% mutate(db = case_when(dbID == 2 ~ "African Pollen DB", dbID == 5 ~ "Latin American Pollen DB")) %>% select(!c(datasetid,primarypub,datecreated.y,datemodified.y,lon,lat,sitename,datasetid,datasettype,dbID)) %>% distinct() %>% group_by(db) %>% mutate(date = as.Date(datecreated.x)) %>%  mutate(year_month = floor_date(date, unit = "month")) %>% group_by(db,year_month) %>% summarize_all(~ sum(is.na(.))) %>% mutate_if(is.numeric, cumsum) %>% pivot_longer(cols=c(3:28),names_to = "parameter",values_to = "num_missing")

ggplot(missing_publications_t) + 
  geom_line(mapping=aes(x=year_month,y=num_missing,col=db)) + 
  facet_wrap(~parameter) + theme_bw()

```

```{r new,echo=FALSE,include=TRUE,message = FALSE, warning=FALSE}

#repospec = content(GET("https://api.neotomadb.org/v2.0/data/dbtables?table=repositoryspecimens&count=false&limit=99999&offset=0"))$data
#repospec_mat = matrix(nrow=length(repospec),ncol=length(repospec[[1]]))

#for (i in seq(length(repospec))) {
#  for (j in seq(length(repospec[[1]]))) {
#    if(!is.null(repospec[[i]][[j]])) {
#      repospec_mat[i,j] = repospec[[i]][[j]] 
#    }
#  }
#}

#repospec_df=as.data.frame(repospec_mat)

#names(repospec_df) = c("datasetid","repositoryid","notes","recdatecreated","recdatemodified")


#repos = content(GET("https://api.neotomadb.org/v2.0/data/dbtables?table=repositoryinstitutions&count=false&limit=99999&offset=0"))$data
#repos_mat = matrix(nrow=length(repos),ncol=length(repos[[1]]))

#for (i in seq(length(repos))) {
#  for (j in seq(length(repos[[1]]))) {
#    if(!is.null(repos[[i]][[j]])) {
#      repos_mat[i,j] = repos[[i]][[j]] 
#    }
#  }
#}

#repos_df=as.data.frame(repos_mat)

#names(repos_df) = c("repositoryid","acronym","repostiory","notes","recdatecreated","recdatemodified")

## Montana State University

#repos_laapd = repospec_df %>% dplyr::filter(datasetid %in% db_sets$datasetid) 

#db_repos_laapd = db_sets %>% dplyr::filter(datasetid %in% repos_laapd$datasetid)

```
<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>