---
title: "APD collection units missing coordinates"
author: "Nick Hoffman"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    highlight: pygment
    keep_md: no
    toc: true
    number_sections: true
    toc_depth: 1
    toc_float: true
    theme: journal
editor_options:
    chunk_output_type: inline
---

<style type="text/css">
h2, h3, h4, h5, h6 {
  counter-reset: section;
}
p {
  font-size:18px;
}

ul {
  font-size:18px;
}

li {
  font-size:18px;
}
table {
   padding: 0;border-collapse: collapse;
   layout: fixed;
   width: 90%; }
table tr {
   border-top: 1px solid #cccccc;
   background-color: white;
   margin: 0;
   padding: 0; }
table tr:nth-child(2n) {
   background-color: #f8f8f8; }
table tr th {
   font-weight: bold;
   border: 1px solid #cccccc;
   margin: 0;
   padding: 6px 13px; }
table tr td {
   border: 1px solid #cccccc;
   margin: 0;
   padding: 6px 13px; }
table tr th :first-child, table tr td :first-child {
   margin-top: 0; }
table tr th :last-child, table tr td :last-child {
   margin-bottom: 0; }
.html-widget {
    margin: auto;
}
</style>

---

```{r, results='asis', echo = F}
toc_depth <- rmarkdown::metadata$output$html_document$toc_depth
sel <- paste0("h",(toc_depth+1):10, collapse = " > span, ")
cat(paste0("<style>",
           sel, 
           " > .header-section-number { display: none; } </style>"))
```


```{r libs, echo=FALSE,warning=FALSE,message=FALSE}

library(wkb)
library(sf)
library(dplyr)
library(httr)
library(leaflet)
library(DT)
library(neotoma2)
library(dplyr)
library(lubridate)
```


```{r downloadtabs, echo=FALSE,warning=FALSE,message=FALSE}


tables = c("dslinks","collectionunits","sites","datasets","publications", "datasetpublications","constituentdatabases","datasetdatabases","dataprocessors","contacts")



for (i in seq(length(tables))) {

  table = tables[[i]]
dslinks = content(GET(paste0("https://api.neotomadb.org/v2.0/data/dbtables?table=",table,"&limit=75000&offset=0")))$data



if (table == "publications") {
  dsl_df = matrix(nrow=length(dslinks),ncol=(length(dslinks[[1]]) - 2))
  for (j in seq(1,length(dslinks))) {
  for (k in seq((length(dslinks[[1]])) - 2)) {
    if (!is.null(dslinks[[j]][[k]])) {
      dsl_df[j,k] = dslinks[[j]][[k]]
    }
  }
}
}
else {
  dsl_df = matrix(nrow=length(dslinks),ncol=length(dslinks[[1]]))
for (j in seq(1,length(dslinks))) {
  for (k in seq(length(dslinks[[1]]))) {
    if (!is.null(dslinks[[j]][[k]])) {
      dsl_df[j,k] = dslinks[[j]][[k]]
    }
  }
}
}

dsl_df = as.data.frame(dsl_df)

if (table =="publications") {
names(dsl_df) = names(dslinks[[1]])[1:(length(dslinks[[1]])-2)]  }

else {
  names(dsl_df) = names(dslinks[[1]])  
}

assign(paste0(table,"_df"), dsl_df)
}




```

```{r dbsets, echo=FALSE,warning=FALSE,message=FALSE}

db_sets = as.data.frame(matrix(nrow=0,ncol=7))
names(db_sets) =c("lon","lat","siteid","sitename","datasetid","datasettype","dbID")
for (i in c(2)) {
 db = content(GET(paste0("https://api.neotomadb.org/v2.0/apps/constdb/datasets?dbid=",i)))$data
    #print(paste("DB ID:",i))
    db_mat = matrix(nrow=length(db),ncol=7)
    for (m in seq(length(db))) {
      if(!is.null(db[[m]]$coords[[1]])) {
        db_mat[[m,1]] = db[[m]]$coords[[1]]}
      if(!is.null(db[[m]]$coords[[2]])) {
        db_mat[[m,2]] = db[[m]]$coords[[2]]}
      if(!is.null(db[[m]]$siteid)) {
        db_mat[[m,3]] = db[[m]]$siteid}
      if(!is.null(db[[m]]$sitename)) {
        db_mat[[m,4]] = db[[m]]$sitename}
      if(!is.null(db[[m]]$datasetid)) {
        db_mat[[m,5]] = db[[m]]$datasetid
      }
        if(!is.null(db[[m]]$datasettype)) {
        db_mat[[m,6]] = db[[m]]$datasettype
        }
      db_mat[[m,7]] = i
    }
    db_df = as.data.frame(db_mat)
    names(db_df) = c("lon","lat","siteid","sitename","datasetid","datasettype","dbID")
    db_sets = rbind(db_sets,db_df)

}
```

# Groups of Missing Collection Unit Coords

## Point Site, Single Collection Unit associated


```{r coll, echo=FALSE,warning=FALSE,message=FALSE}


apd_colls = collectionunits_df %>% dplyr::filter(siteid %in% db_sets$siteid)

apdcolls_missingloc = apd_colls %>% left_join(db_sets, by=join_by(siteid)) %>% dplyr::filter(dbID ==2) %>% dplyr::filter(is.na(gpslatitude)) %>% dplyr::select(!c(datasettype,datasetid)) %>% distinct()


datatable(apdcolls_missingloc,rownames=FALSE)

apd_sites = sites_df %>% dplyr::filter(siteid %in% db_sets$siteid)


apd_sfc = st_as_sfc(hex2raw(apd_sites$geog),EWKB=TRUE)
apd_sites_sf = st_as_sf(apd_sites,geom=apd_sfc) %>% dplyr::select(!geog)

site_coll_count = apd_sites_sf %>% left_join(collectionunits_df, by=join_by(siteid)) %>% dplyr::filter(!is.na(collectionunitid)) %>% group_by(siteid) %>% count()

site_coll_singlepoints = site_coll_count %>% dplyr::filter(n ==1 & st_geometry_type(geom) == "POINT")

singlepoints = apd_sites_sf %>% dplyr::filter(siteid %in% c(site_coll_singlepoints$siteid)) %>% left_join(apd_colls, by=join_by(siteid)) %>% dplyr::filter(is.na(gpslongitude) & is.na(gpslatitude)) %>% dplyr::mutate(siteid=as.numeric(siteid))

clip_spt = singlepoints %>% arrange(desc(siteid)) 



spt_pubs = singlepoints %>% left_join(datasets_df, by=join_by(collectionunitid)) %>% left_join(datasetpublications_df, by=join_by(datasetid)) %>% left_join(publications_df,by=join_by(publicationid))

writeClipboard(paste(clip_spt$geom, collapse = "\n"))

```

There are `r length(singlepoints[[1]])` collection units that are uniquely associated with a site, and the site has a point geometry. (That is, the point site has just one collection unit.) For these `r length(singlepoints[[1]])` collection units, it seems reasonable to assume that the collection unit's coordinates should be the same as the site's coordinates. 

```{r datatablesingpoint3, echo=FALSE,warning=FALSE,message=FALSE}
datatable(singlepoints,rownames=FALSE)


    leaflet() %>%
  addTiles() %>%
  addCircleMarkers(data = singlepoints, 
                   radius = 5, 
                   color = "blue", 
                   fillColor = "blue", 
                   fillOpacity = 0.2, 
                   stroke = FALSE, 
                   popup = ~sitename)


```

## Polygon Site, Single Collection Unit Associated

```{r polysingle, echo=FALSE,warning=FALSE,message=FALSE}


site_coll_singlepoly = site_coll_count %>% dplyr::filter(n ==1 & st_geometry_type(geom) == "POLYGON")

singlepolys = apd_sites_sf %>% dplyr::filter(siteid %in% c(site_coll_singlepoly$siteid)) %>% left_join(apd_colls, by=join_by(siteid)) %>% dplyr::filter(is.na(gpslongitude) & is.na(gpslatitude))



singpol_pubs = singlepolys %>% left_join(datasets_df, by=join_by(collectionunitid)) %>% left_join(datasetpublications_df, by=join_by(datasetid)) %>% left_join(publications_df,by=join_by(publicationid))

distinct_spolp = singpol_pubs %>% distinct(publicationid)



clip_spolt = singlepolys %>% arrange(desc(siteid)) 



spol_pubs = singlepolys %>% left_join(datasets_df, by=join_by(collectionunitid)) %>% left_join(datasetpublications_df, by=join_by(datasetid)) %>% left_join(publications_df,by=join_by(publicationid))

writeClipboard(paste(clip_spolt$siteid, collapse = "\n"))


```

There are `r length(singlepolys[[1]])` collection units that are uniquely associated with a site, and the site has a polygon geometry. (That is, the polygon site has just one collection unit.) For these `r length(singlepolys[[1]])` collection units, I should investigate the `r length(distinct_spolp[[1]])` associated papers and see if there are more precise coordinates associated with these.

```{r datatablesingpoly4, echo=FALSE,warning=FALSE,message=FALSE}
datatable(singlepolys,rownames=FALSE)


    leaflet() %>%
  addTiles() %>%
  addPolygons(data = singlepolys, 
              color = "red", 
              weight = 8, 
              fillColor = "orange", 
              fillOpacity = 0.35, 
              popup = ~sitename)  



datatable(st_drop_geometry(singpol_pubs[c('siteid','sitename','collectionunitid','collunitname','datasetid','citation')]))

```

## Point site, multiple collection units associated



```{r coll22, echo=FALSE,warning=FALSE,message=FALSE}


site_coll_multipoints = site_coll_count %>% dplyr::filter(n >1 & st_geometry_type(geom) == "POINT")

multipoints = apd_sites_sf %>% dplyr::filter(siteid %in% c(site_coll_multipoints$siteid)) %>% left_join(apd_colls, by=join_by(siteid)) %>% dplyr::filter(is.na(gpslongitude) & is.na(gpslatitude)) 

##%>% left_join(datasets_df, by=join_by(collectionunitid)) %>% left_join(datasetdatabases_df, by=join_by(datasetid)) %>% left_join(constituentdatabases_df, by=join_by(databaseid))

multipoint_sites = multipoints %>% distinct(siteid)




multipoint_pubs = multipoints %>% left_join(datasets_df, by=join_by(collectionunitid)) %>% left_join(datasetpublications_df, by=join_by(datasetid)) %>% left_join(publications_df,by=join_by(publicationid))

distinct_mpntp = multipoint_pubs %>% distinct(publicationid)

```



There are `r length(multipoints[[1]])` collection units that are jointly associated with a site (n = `r length(multipoint_sites[[1]])`), and the site has a point geometry. (That is, the point site has multiple collection units.) For these `r length(multipoints[[1]])` collection units, I should investigate the associated `r length(distinct_mpntp[[1]])` papers and see if there are more precise coordinates associated with these. But I'm wondering if there's a kind of logical problem with having multiple collectionunits associated with a point site: in a way, doesn't that require that all the collectionunits have the same location (i.e., the location of the single site point)?

```{r datatablesingpoly1, echo=FALSE,warning=FALSE,message=FALSE}
datatable(multipoints,rownames=FALSE)


    leaflet() %>%
  addTiles() %>%
  addCircleMarkers(data = multipoints, 
              color = "blue", 
              radius = 5, 
              fillColor = "blue", 
              fillOpacity = 0.35, 
              popup = ~sitename)  


datatable(st_drop_geometry(multipoint_pubs[c('siteid','sitename','collectionunitid','collunitname','datasetid','citation')]))

```


## Poly site, multiple collection units associated




```{r coll21, echo=FALSE,warning=FALSE,message=FALSE}


site_coll_multipolys = site_coll_count %>% dplyr::filter(n >1 & st_geometry_type(geom) == "POLYGON")

multipolys = apd_sites_sf %>% dplyr::filter(siteid %in% c(site_coll_multipolys$siteid)) %>% left_join(apd_colls, by=join_by(siteid)) %>% dplyr::filter(is.na(gpslongitude) & is.na(gpslatitude)) 

##%>% left_join(datasets_df, by=join_by(collectionunitid)) %>% left_join(datasetdatabases_df, by=join_by(datasetid)) %>% left_join(constituentdatabases_df, by=join_by(databaseid))

multipoly_sites = multipolys %>% distinct(siteid)


multipoly_pubs = multipolys %>% left_join(datasets_df, by=join_by(collectionunitid)) %>% left_join(datasetpublications_df, by=join_by(datasetid)) %>% left_join(publications_df,by=join_by(publicationid))

distinct_mpp = multipoly_pubs %>% distinct(publicationid)

```



There are `r length(multipolys[[1]])` collection units that are jointly associated with a site (n = `r length(multipoly_sites[[1]])`), and the site has a polygon geometry. (That is, the polygon site has multiple collection units.) For these `r length(multipolys[[1]])` collection units, I should investigate the associated `r length(distinct_mpp[[1]])`` papers and see if there are more precise coordinates associated with these.

```{r datatablesingpoly2, echo=FALSE,warning=FALSE,message=FALSE}
datatable(multipolys,rownames=FALSE)


    leaflet() %>%
  addTiles() %>%
  addPolygons(data = multipolys, 
              color = "red", 
              weight = 8, 
              fillColor = "orange", 
              fillOpacity = 0.35, 
              popup = ~sitename)  




datatable(st_drop_geometry(multipoly_pubs[c('siteid','sitename','collectionunitid','collunitname','datasetid','citation')]))

```

48868 is an NA microcharcoal
48865 and 48874 are duplicate microcharcoal
48866 is NA pollen

```{r vankervels}

dslinks_df=dslinks_df %>% dplyr::mutate(datasetid = as.character(datasetid),collectionunitid = as.character(collectionunitid))
vanker =dslinks_df %>% dplyr::filter(siteid=="26668") %>% dplyr::left_join(datasets_df) %>% dplyr::left_join(collectionunits_df,by=join_by(collectionunitid)) %>% left_join(dataprocessors_df,by=join_by(datasetid)) %>% left_join(contacts_df,by=join_by(contactid))

ds = get_datasets(c(as.numeric(vanker$datasetid)),all_data=TRUE)

vanker_data = get_downloads(ds,all_data=TRUE) %>% samples()


counts = vanker_data %>% group_by(datasetid,datasettype) %>% count()

varicount = vanker_data %>% group_by(datasetid,datasettype) %>% summarize(toString(unique(variablename))) %>% left_join(counts)


vanker_data %>% dplyr::filter(datasetid %in% c("46706","48865","48868","48874"))

who =vanker %>% dplyr::mutate(date = as.Date(recdatecreated.x)) %>% select(datasetid,contactname,date)

vanker_data %>% group_by(datasetid) %>% summarize(datasettype) %>% distinct() %>% left_join(who) %>% left_join(varicount) %>% datatable(rownames=FALSE)
 ```
<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>