---
title: "LAPD sites missing location"
author: "Nick Hoffman"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    highlight: pygment
    keep_md: no
    theme: journal
editor_options:
    chunk_output_type: inline
---

<style type="text/css">
h2, h3, h4, h5, h6 {
  counter-reset: section;
}
p {
  font-size:18px;
}

ul {
  font-size:18px;
}

li {
  font-size:18px;
}
table {
   padding: 0;border-collapse: collapse;
   layout: fixed;
   width: 90%; }
table tr {
   border-top: 1px solid #cccccc;
   background-color: white;
   margin: 0;
   padding: 0; }
table tr:nth-child(2n) {
   background-color: #f8f8f8; }
table tr th {
   font-weight: bold;
   border: 1px solid #cccccc;
   margin: 0;
   padding: 6px 13px; }
table tr td {
   border: 1px solid #cccccc;
   margin: 0;
   padding: 6px 13px; }
table tr th :first-child, table tr td :first-child {
   margin-top: 0; }
table tr th :last-child, table tr td :last-child {
   margin-bottom: 0; }
.html-widget {
    margin: auto;
}
</style>

---

```{r lib, echo=FALSE,warning=FALSE,message=FALSE}

library(readxl)
library(httr)
library(dplyr)
library(neotoma2)
library(DT)
library(tidyverse)

```

This data table has most of the right coordinates:

```{r setup, echo=FALSE,warning=FALSE,message=FALSE}



db_sets = as.data.frame(matrix(nrow=0,ncol=7))
names(db_sets) =c("lon","lat","siteid","sitename","datasetid","datasettype","dbID")
for (i in c(2,5)) {
    db = content(GET(paste0("https://api.neotomadb.org/v2.0/apps/constdb/datasets?dbid=",i)))$data
    #print(paste("DB ID:",i))
    db_mat = matrix(nrow=length(db),ncol=7)
    for (m in seq(length(db))) {
        if(!is.null(db[[m]]$coords[[1]])) {
            db_mat[[m,1]] = db[[m]]$coords[[1]]}
        if(!is.null(db[[m]]$coords[[2]])) {
            db_mat[[m,2]] = db[[m]]$coords[[2]]}
        if(!is.null(db[[m]]$siteid)) {
            db_mat[[m,3]] = db[[m]]$siteid}
        if(!is.null(db[[m]]$sitename)) {
            db_mat[[m,4]] = db[[m]]$sitename}
        if(!is.null(db[[m]]$datasetid)) {
            db_mat[[m,5]] = db[[m]]$datasetid
        }
        if(!is.null(db[[m]]$datasettype)) {
            db_mat[[m,6]] = db[[m]]$datasettype
        }
        db_mat[[m,7]] = i
    }
    db_df = as.data.frame(db_mat)
    names(db_df) = c("lon","lat","siteid","sitename","datasetid","datasettype","dbID")
    db_sets = rbind(db_sets,db_df)
    
}

sites = content(GET("https://api.neotomadb.org/v2.0/data/dbtables/sites?count=false&limit=99999"))$data



site_mat = matrix(nrow=length(sites),ncol=13)

for (i in seq(length(sites))) {
    for(j in seq(13) ) {
        if (!is.null(sites[[i]][[j]])) {
            site_mat[i,j] = sites[[i]][[j]]
        }}}


site_df = as.data.frame(site_mat)


names(site_df) = c("siteid","sitename","longitudeeast","latitudenorth","longitudewest","latitudesouth","altitude","area","sitedescription","notes","datecreated","datemodified","geog")
alapd_sites = site_df %>% dplyr::filter(siteid %in% db_sets$siteid)

no_loc = alapd_sites %>% dplyr::filter(is.na(longitudeeast))


bush2020 = read_xlsx("All_Appendices_R3_Simplified.xlsx",sheet=2) %>% dplyr::filter(`site name` %in% no_loc$sitename) %>% dplyr::select(`sample number`,`site name`,latitude,longitude) %>% distinct()

datatable(bush2020, rownames=FALSE)

```

However, there are two issues to deal with. First, multiple sites named Darien have different lat/lons. I mapped Neotoma site ids to spreadsheet id ("sample number") by joining pollen counts in Neotoma to spreadsheet pollen counts by Alchornea, which has distinct values for all Dariens in either source.

```{r nextprob, echo=FALSE,warning=FALSE,message=FALSE}


darien_siteid = no_loc %>% dplyr::filter(sitename=="Darien") %>% distinct(siteid)
## 29847, 29891, 29883, 29889
r_sites = get_sites(c(29847, 29891, 29883, 29889), all_data=TRUE)

darien_poll = get_datasets(r_sites,all_data=TRUE) %>% get_downloads(all_data=TRUE) %>% samples()

pollcounts = darien_poll %>% pivot_wider(id_cols=c(siteid,age),names_from="variablename",values_from=value)

pollcounts = sapply(pollcounts, function(x) replace(x, is.na(x), 0)) %>% as.data.frame()

bush2020_poll = read_xlsx("All_Appendices_R3_Simplified.xlsx",sheet=3) %>% dplyr::filter(`site name` == "Darien")

darien_map = pollcounts %>% dplyr::mutate(Alchornea = as.numeric(Alchornea)) %>% left_join(bush2020_poll, by= join_by(Alchornea)) %>% dplyr::select(siteid, `sample number`,`site name`) %>% left_join(bush2020)


datatable(darien_map,rownames=FALSE)

```

The second problem to deal with is that one of the Neotoma site names (Cuyabeno) isn't in the spreadsheet, even though the metadata says it should be and similar names are. I took a similar tactic of getting Cuyabeno's pollen count and joining to the spreadsheet table, this time on the basis of every pollen field that Cuyabeno has. I found that Cuyabeno == Cuyabeno_1

```{r ohagain, echo=FALSE,warning=FALSE,message=FALSE}

missingsite = no_loc %>% dplyr::filter(!sitename %in% bush2020$`site name`)

missing_siteid = no_loc %>% dplyr::filter(sitename=="Cuyabeno") %>% distinct(siteid)
## 29849
missing_site = get_sites(c(29849), all_data=TRUE)


missing_poll = get_datasets(missing_site,all_data=TRUE) %>% get_downloads(all_data=TRUE) %>% samples()

misscounts = missing_poll %>% mutate(value = as.numeric(value)) %>% pivot_wider(id_cols=c(siteid,sitename,datasetid,age),names_from="variablename",values_from=value)

misscounts = sapply(misscounts, function(x) replace(x, is.na(x), 0)) %>% as.data.frame()


misscounts[3:length(misscounts)] <- sapply(misscounts[3:length(misscounts)], function(x) as.numeric(as.character(x)))


bush2020_look = read_xlsx("All_Appendices_R3_Simplified.xlsx",sheet=3)


miss_name = misscounts %>% left_join(bush2020_look) %>% dplyr::select(siteid,sitename,`sample number`,`site name`,)

miss_loc = read_xlsx("All_Appendices_R3_Simplified.xlsx",sheet=2) %>% dplyr::filter(`site name` == miss_name$`site name`) %>% left_join(miss_name) %>% dplyr::select(`sample number`, `site name`, sitename, latitude, longitude) %>% distinct()


datatable(miss_loc,rownames=FALSE)

```

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
